Linear analysis of the vertical shear instability in astrophysical disks

### 2014-12-29 linear_adia.tex
updated analytical discussion

Fig. \ref{relax_disp_fig}---\ref{relax_bcrit} shows that a growing fundamental
VSI mode exists both in the isothermal ($\beta\to0$) and adiabatic
($\beta\to\infty$) limits, although the latter growth rates are
smaller by at least a factor of two. Furthermore, the adiabatic VSI is 
is limited to a thin layer about the disk midplane so it may be
considered stable. Then Fig. \ref{relax_bcrit} shows that 
$\beta\lesssim 0.1$ is required for instability in this disk model. This critical
timescale is indepedent of $k_x$ for
$k_xH_\mathrm{iso}\gtrsim10$. Fig. \ref{relax_disp_fig} is also consistent with previous
discussions which show that thermal relaxation has no effect for
$k_x\to0$ or $k_x\to\infty$ as $\beta\to0$,

>>>>

Fig. \ref{relax_disp_fig}---\ref{relax_bcrit} shows that a growing fundamental
VSI mode exists both in the isothermal ($\beta\to0$) and adiabatic
($\beta\to\infty$) limits, although the latter growth rates are
smaller by at least a factor of two. Furthermore, the adiabatic VSI is 
is limited to a thin layer about the disk midplane so it may be
considered stable. Then Fig. \ref{relax_bcrit} shows that 
$\beta\lesssim 0.1$ is required for instability in this disk model. This critical
timescale is indepedent of $k_x$ for
$k_xH_\mathrm{iso}\gtrsim10$. The top panel of Fig. \ref{relax_disp_fig} is also
consistent with the previous
discussion that show thermal relaxation has no effect for
$k_x\to0$ or $k_x\to\infty$ as $\beta\to0$.
